Supplementary Information 1

### 2025-03-27 index.Rmd
adding stest to MSE

---
title: "Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations"
subtitle: "Working Paper to be submitted in a CCAMLR EMM-WG 2024"
author: "Mardones, M; Cárdenas, C., Krüger, L., Santa Cruz, F."
date:  "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: SA_krill.bib
csl: apa.csl
link-citations: yes
linkcolor: blue
output:
  html_document:
    keep_md: true
    toc: true
    toc_deep: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    fontsize: 0.9em
    linestretch: 1.7
    html-math-method: katex
    self-contained: true
    code-tools: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup1, echo=FALSE}
#rm(list = ls())
#set.seed(999)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      fig.pos = "H",
                      dev = 'jpeg',
                      dpi = 300,
                      tidy.opts=list(width.cutoff=50), 
                      tidy=TRUE)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```

```{r message=FALSE, eval=TRUE}
# install.packages("devtools")
# devtools::install_github("r4ss/r4ss", ref="development")
# install.packages("caTools")
# library("caTools")
# install.packages("r4ss")
library(r4ss)
library(here)
#remotes::install_github("PIFSCstockassessments/ss3diags")
library(ss3diags)
library(kableExtra)
library(doParallel) # facilita la ejecución paralela en R
detectCores()
registerDoParallel(8)
library(ggpubr)
library(tibble)
library(openxlsx)
library(ggthemes)
library(forecast)
library(tidyr)
library(mixR)
library(readxl)
```

```{r message=FALSE, warning=FALSE, echo=TRUE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # without S-R
dir4<-here("s4") # 
dir5<-here("s5") # 
dir6<-here("s6") # 
dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
dir8<-here("s8") # s1 platoons
dir9<-here("s9") # s1 w/ blocks
dir1.1<-here("s1.1") # con todo
dir1.2 <- here("s1.2") # sin predador ni ambiental
dir1.3 <- here("s1.3") # borrado los registros de prreddador )igual q el S2
Figs <- here("Figs")# S
```

# OVERVIEW

In a simple way, the core of Stock Synthesis is its population dynamics
model, which represents the dynamics of krill populations over time.
This model incorporates key biological, environmental and predator data
sources. The model is typically formulated using mathematical equations
that describe how these parameters interact to determine the abundance
and distribution of krill in the study area.

## Statistical model (SS3)

Stock Synthesis v.3.30.21 is a widely used software tool for assessing
fish and invertebrate populations, including krill (Euphausia superba)
in the Antarctic Peninsula region. The methodology employed by Stock
Synthesis involves a comprehensive and integrated approach, utilizing
various data sources and modeling techniques to estimate the main
population variables of krill in WAP.

The stock assesment model was configured using Stock Synthesis (SS3
hereafter)[SS3](https://vlab.noaa.gov/web/stock-synthesis) [@Methot2013;
@methot2020stock] with the most updated version (V.3.30.21). SS3 is a
structured age and size stock evaluation model, in the class of models
called *"Integrated stock evaluation analysis model"*. SS3 has a stock
population sub-model that simulates growth, maturity, fecundity,
recruitment, movement, and mortality processes, and observation
sub-models and expected values for different types of data. The model is
coded in `C++` with estimation parameters enabled by automatic
differentiation (ADMB) [@Fournier2012; @Methot2013]. The analysis of
results and outputs uses R tools and the graphical interface of the
*r4ss* and *ss3diags* library [@Taylor2019; @Winker2023].

By integrating data from multiple sources and considering spatial
heterogeneity, the assessment methodology using Stock Synthesis
v.3.30.21 provides a robust framework for evaluating the status of krill
populations in the Antarctic Peninsula region. This information is
essential for supporting management decisions aimed at ensuring the
sustainable use of krill resources in this ecologically sensitive area.

## Parametres

read files

```{r}
# leo archivos para plotear y hacer tablas
start1 <- SS_readstarter(file = file.path(dir1.1,
                                          "starter.ss"),
                              verbose = FALSE)
# note the data and control file names can vary, so are determined from the 
# starter file.
dat1 <- SS_readdat(file = file.path(dir1.1, start1$datfile),
                        verbose = FALSE)
# Read in ctl file. Note that the data fileR object is needed so that SS_readctl
# assumes the correct data structure
ctl1 <-  r4ss::SS_readctl(file = file.path(dir1.1,
                                    start1$ctlfil),
                        verbose = FALSE,
                        use_datlist = TRUE, 
                   datlist = dat1)
fore1 <- r4ss::SS_readforecast(file = file.path(dir1.1, 
                                                "forecast.ss"),
                              verbose = FALSE)
# can also read in wtatage.ss for an empirical wt at age model using
# r4ss::SS_readwtatage()
```

@@

 SRpar<-ctl1$SR_parms[1:5,c(1:3,7)]
 Qpar<-ctl1$Q_parms[1:2,c(1:3,7)]
 Selpar<-ctl1$size_selex_parms[1:22,c(1:3,7)]
 parInit<-as.data.frame(rbind(parbio,SRpar,Qpar,Selpar))
```

```{r eval=FALSE}
wb <- createWorkbook()

@@

# Guardar el workbook
saveWorkbook(wb, "DataKrill.xlsx", overwrite = TRUE)

@@

```{r}
parInit %>%
  mutate(across(where(is.numeric), ~ round(., 3)))  %>% 
  kbl(booktabs = TRUE,
      format = "html",
      position = "ht!",
      caption = "Input parameters for the initial SS3 model of krill. Each parameter line contains a minimum value (LO), maximum value (HI), and initial value (INIT). If the phase (PHASE) for the parameter is negative, the parameter is fixed as input") %>%
  kable_paper("hover", full_width = TRUE) %>%  # Expande el ancho
  kable_styling(latex_options = c("striped", "condensed"),
                full_width = TRUE,  # Expande la tabla al ancho completo
                font_size = 12,
                html_font = "Times New Roman") %>%  # Aplica la fuente Times New Roman
  pack_rows(index = c("Mortalidad natural" = 1,
                      "Crecimiento" = 5,
                      "Relación longitud-peso" = 2,
                      "Ojiva de madurez" = 2,
                      "Relación stock-recluta" = 5,
                      "Capturabilidad" = 2,
                      "Selectividad" = 4))

@@

| Scenario | Description                                                                          |
|:------------:|:---------------------------------------------------------|
|   s01    | Fishery and Survey (AMLR) data, Predator, Environmental aggregate data in 48.1       |
|    s1    | Fishery and Survey (AMLR) data Length, Index, Catch by strata. Predator and Env data |
|    s2    | "s1" without S-R relation                                                            |
|    s3    | "s1" BH S-R relation weak (0.9 steepness)                                            |
|    s4    | "s1" BH S-R relation strong (0.6 steepness)                                          |
|    s5    | "s1" BH S-R relation mid-strong estimated                                            |
|    s6    | "s1" Ricker S-R relation estimated                                                   |
|    s7    | "s1" w/ set of parameters estimated in @EMM-204/32                                   |
|    s8    | "s1" test data weighting                                                             |
|    s9    | "s1" w/ selectivity blocks                                                           |
|    s1.1  | Spatial data without environmental and predator components                          |
|    s1.2  | "s1.1" with environmental and predator components                                    |
|    s1.3  | "s1.2" w/ selectivity blocks                                                         |

@@

base.model1.1 <- SS_output(dir=dir1.1,
                        covar=T,
                        forecast=T)
```

Read outputs

```{r message=F, include=FALSE}

#s1.1
base.model1.1 <- SS_output(dir=dir1.1,
                        covar=T,
                        forecast=T)
#s1.2
base.model1.2 <- SS_output(dir=dir1.2,
                        covar=T,
                        forecast=T)
#s1.3
base.model1.3 <- SS_output(dir=dir1.3,
                        covar=T,
                        forecast=T)
```

```{r}
SSplotTimeseries(base.model1.1,
                 subplot = 1)
SSplotTimeseries(base.model1.1,
                 subplot = 9)
SSplotTimeseries(base.model1.1,
                 subplot = 7)
```
and fits

@@

```{r}
SSplotComps(base.model1.1,
            subplots = 1)

@@

# RESULTS
```{r eval=FALSE, message=F, include=FALSE}
# Definir la ruta de la carpeta
folder_path <- "s1.1/plots"
# Verificar si la carpeta existe y eliminarla
if (dir.exists(folder_path)) {
  unlink(folder_path, recursive = TRUE)
  message("La carpeta 'plots' ha sido eliminada.")
} else {
  message("La carpeta 'plots' no existe.")
}

SS_plots(base.model1.1, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

### Main Variables poulation

@@

```{r eval=FALSE}
total01 <- as.data.frame(base.model01$timeseries[1:50,c(2,5)]) %>%
  mutate(Serie = "No Spatial")
total1 <- as.data.frame(base.model1$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial implicit")
total2 <- as.data.frame(base.model2$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ without S-R relation")
total3 <- as.data.frame(base.model3$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation weak (0.9 steepness)")
total4 <- as.data.frame(base.model4$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation strong (0.6 steepness)")
total5 <- as.data.frame(base.model5$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation mid-strong estimated ")
total6 <- as.data.frame(base.model6$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ Ricker S-R relation estimated")
total7 <- as.data.frame(base.model7$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ New set parameters Linf, k and M")

@@

```{r }
SSplotData(base.model1.1, 
           subplot = 1,
           pheight = 15)
```

Respecto a los valores y parametros biologicos modelados, los siguientes
graficos identifican los estimadores puntuales del recurso

```{r fig.height=6}
SSplotSelex(base.model01,
            subplots = 1)
SSplotSelex(base.model1,
            subplots = 1)
SSplotSelex(base.model2,
            subplots = 1)
SSplotSelex(base.model3,
            subplots = 1)
SSplotSelex(base.model4,
            subplots = 1)
SSplotSelex(base.model5,
            subplots = 1)
SSplotSelex(base.model6,
            subplots = 1)
SSplotSelex(base.model1.1,
            subplots = 1)
```

@@

```{r}
SSplotRunstest(base.model1.1,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

@@

```{r}
SSplotRunstest(base.model1.1,
               subplots = "cpue",
               add=T)
```

@@

```{r eval=FALSE}
SSplotJABBAres(base.model01,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.1,
               subplots = "len",
               add=T)
```

```{r}
SSplotJABBAres(base.model01,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.1,
               subplots = "cpue",
               add=T)
```
## Relationship Stock-Recruit

@@

## Likelihood

@@

```{r echo=FALSE}
#read in all model runs
#note if cover=T you need a hessian; if covar=F you do not need a hessian
biglist01_1_7 <- SSgetoutput(keyvec = NULL,
                       dirvec = c(
                                  dir01,
                                  dir1,
                                  dir7),
                       getcovar = F)

#create summary of model runs from list above
summaryoutput01_1_7 <- SSsummarize(biglist01_1_7)

SSplotComparisons(summaryoutput01_1_7,
                  legendlabels = c(
                                   "No Spatial",

                 "Spatial",
                 "Spatial w/ new set LH paramters"),
                 filenameprefix = "COM1",
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)
```

>>>>

---
title: "Supplementary Information 1"
subtitle: "Assessing ecosystem effects on the stock productivity of Antarctic Krill (*Euphausia superba*): An Integrated modeling perspective"
author: "Mardones, M; Jarvis Mason, E.T.; Pinones, A.;  Santa Cruz, F.; Cárdenas, C.A"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: SA_krill.bib
#csl: apa.csl
csl: icesjournal.csl
link-citations: yes
linkcolor: blue
output:
  html_document:
    keep_md: true
    toc: true
    toc_deep: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    fontsize: 0.9em
    linestretch: 1.7
    html-math-method: katex
    self-contained: true
    code-tools: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup1, echo=FALSE}
#rm(list = ls())
#set.seed(999)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      fig.pos = "H",
                      dev = 'jpeg',
                      fig.path = "Figs/",
                      dpi = 300,
                      tidy.opts=list(width.cutoff=50), 
                      tidy=TRUE)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```

```{r message=FALSE, eval=TRUE}
# install.packages("devtools")
# devtools::install_github("r4ss/r4ss", ref="development")
# install.packages("caTools")
# library("caTools")
# install.packages("r4ss")
library(r4ss)
library(here)
#remotes::install_github("PIFSCstockassessments/ss3diags")
library(ss3diags)
library(kableExtra)
library(doParallel) # facilita la ejecución paralela en R
detectCores()
registerDoParallel(8)
library(ggpubr)
library(tibble)
library(openxlsx)
library(ggthemes)
library(forecast)
library(tidyr)
library(mixR)
library(readxl)
library(tidyverse)
library(ggridges)
```

```{r message=FALSE, warning=FALSE, echo=TRUE}
# dir01 <- here("s01") # agreggate data (no spatial diferences)
# dir1<-here("s1") # Data strata flishery
# dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
# dir3<-here("s3") # without S-R
# dir4<-here("s4") # 
# dir5<-here("s5") # 
# dir6<-here("s6") # 
# dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
# dir8<-here("s8") # s1 platoons
# dir9<-here("s9") # s1 w/ blocks
dir1.1<-here("s1.1") # con todo
dir1.2 <- here("s1.2") # sin predador ni ambiental
dir1.3 <- here("s1.3") # borrado los registros de prreddador )igual q el S2
Figs <- here("Figs")# S
```

## Overview

This study aims to evaluate the impact of ecosystem components—such as environmental variables and predator-prey interactions—on the productivity and key population dynamics of *Euphausia superba* in Subarea 48.1. By incorporating these factors into the assessment, we analyze how krill population variables respond to ecological variability, providing insights into their resilience and potential management implications.

Here, the **reference model** represents a baseline assessment of *Euphausia superba* population dynamics in Subarea 48.1, excluding environmental and ecological variables. This model assumes that krill productivity and population parameters are driven  by intrinsic biological processes, such as growth, mortality, and recruitment and fishery impacts without accounting for external influences like environmental variability or predation pressure. By serving as a *control scenario*, this model provides a benchmark against which the impact of ecosystem components in productivity can be evaluated, allowing for a direct comparison of how environmental and ecological factors influence krill stock dynamics.

## Statistical Model (SS3)

Stock Synthesis (v.3.30.21)  is a widely used tool for assessing fish and invertebrate populations, including Antarctic krill. SS3 is implemented in `C++` with estimation enabled through automatic differentiation (ADMB) [@Fournier2012; @Methot2013]. In this exercise, SS3 is configured as an integrated stock assessment model, explicitly accounting for age and size structure while incorporating key ecosystem drivers. The model simulates population processes such as growth, maturity, fecundity, recruitment, movement, and mortality, while also integrating environmental variability and predator-prey relationships to refine estimates of population trends. The analysis of model outputs is conducted using R, utilizing the *r4ss* and *ss3diags* packages [@Taylor2019; @Winker2023]. By leveraging a spatially implicit, ecosystem-informed approach, this assessment provides a robust framework for evaluating krill stock dynamics under changing environmental conditions. These insights are crucial for informing sustainable management strategies in the Antarctic Peninsula region, where krill plays a foundational role in the marine food web.

## Parameters

The following table summarizes the key parameters to conditioning the reference model, including biological, growth, and population dynamics factors.

```{r}
start1 <- SS_readstarter(file = file.path(dir1.1,
                                          "starter.ss"),
                              verbose = FALSE)
dat1 <- SS_readdat(file = file.path(dir1.2, start1$datfile),
                        verbose = FALSE)
ctl1 <-  r4ss::SS_readctl(file = file.path(dir1.1,
                                    start1$ctlfil),
                        verbose = FALSE,
                        use_datlist = TRUE, 
                   datlist = dat1)
fore1 <- r4ss::SS_readforecast(file = file.path(dir1.1, 
                                                "forecast.ss"),
                              verbose = FALSE)
# can also read in wtatage.ss for an empirical wt at age model using
# r4ss::SS_readwtatage()
```

@@

 SRpar<-ctl1$SR_parms[1:5,c(1:3,7)]
 Qpar<-ctl1$Q_parms[1:2,c(1:3,7)]
 Selpar<-ctl1$size_selex_parms[1:22,c(1:3,7)]
 parInit<-as.data.frame(rbind(parbio,SRpar,Qpar,Selpar))

wb <- createWorkbook()

@@

# Guardar el workbook
#saveWorkbook(wb, "DataKrill.xlsx", overwrite = TRUE)

@@

```{r}
parInit %>%
  mutate(across(where(is.numeric), ~ round(., 3)))  %>% 
  kbl(booktabs = TRUE,
      format = "html",
      position = "ht!",
      caption = "Input parameters for the initial SS3 model of krill. Each parameter line contains a minimum value (LO), maximum value (HI), and initial value (INIT). If the phase (PHASE) for the parameter is negative, the parameter is fixed as input") %>%
  kable_paper("hover", full_width = TRUE) %>%  # Expande el ancho
  kable_styling(latex_options = c("striped", "condensed"),
                full_width = TRUE,  # Expande la tabla al ancho completo
                font_size = 12,
                html_font = "Times New Roman") %>%  # Aplica la fuente Times New Roman
  pack_rows(index = c("Natural Mortality" = 1,
                      "Growth" = 5,
                      "relationship Length-Weigth" = 2,
                      "Maturity" = 2,
                      "S-R relation" = 5,
                      "Catchability" = 2,
                      "Selectivity" = 4))

```
Source of data inpit

```{r fig.width=9, fig.height=4}
dat1_std <- dat1$CPUE %>%
  group_by(index) %>%
  mutate(index_std = obs / mean(obs, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(index = recode(index,
                        `1` = "FISHERYBS",
                        `2` = "FISHERYEI",
                        `3` = "FISHERYGS",
                        `4` = "FISHERYJOIN",
                        `5` = "FISHERYSSIW",
                        `6` = "SURVEYBS",
                        `7` = "SURVEYEI",
                        `8` = "SURVEYGS",
                        `9` = "SURVEYJOIN",
                        `10` = "SURVEYSSIW",
                        `11` = "PREDATOR"))
ggplot(dat1_std, aes(x = year, y = index_std, group=index))+
  geom_point() +
  geom_smooth(method="lm",
              se=F)+
  facet_wrap(.~index,
             scales = "free_y",
             ncol=6)+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1))+
  labs(title = "",
       x = "",
       y = "Standar index",
       color = "index")
```

```{r fig.width=10, fig.height=4}
dat_long <- dat1$lencomp %>% 
  pivot_longer(cols = starts_with("l"),  
               names_to = "Talla",  
               values_to = "Frecuencia") %>% 
  mutate(Talla = as.numeric(sub("l", "", Talla))) %>%  
  mutate(FltSvy = recode(FltSvy,
                         `1` = "FISHERYBS",
                         `2` = "FISHERYEI",
                         `3` = "FISHERYGS",
                         `4` = "FISHERYJOIN",
                         `5` = "FISHERYSSIW",
                         `6` = "SURVEYBS",
                         `7` = "SURVEYEI",
                         `8` = "SURVEYGS",
                         `9` = "SURVEYJOIN",
                         `10` = "SURVEYSSIW",
                         `11` = "PREDATOR")) %>%
  mutate(FltSvy = factor(FltSvy, levels = c("FISHERYBS", 
                                            "FISHERYEI", 
                                            "FISHERYGS",
                                            "FISHERYJOIN", 
                                            "FISHERYSSIW",
                                            "SURVEYBS",
                                            "SURVEYEI", 
                                            "SURVEYGS", 
                                            "SURVEYJOIN",
                                            "SURVEYSSIW",
                                            "PREDATOR")))

mean_talla <- dat_long %>%
  group_by(FltSvy) %>%
  summarise(mean_Talla = mean(Talla, na.rm = TRUE))

# Expandir datos según la frecuencia
dat_expanded <- dat_long %>%
  uncount(weights = Frecuencia)

# Crear el gráfico con líneas verticales en cada facet
ggplot(dat_expanded, aes(x = Talla, y = as.factor(Yr), 
                         fill = stat(x))) +
  geom_density_ridges_gradient(scale = 1.8,
                               rel_min_height = 0.001,
                               col = "black",
                               fill = "grey") +
  facet_wrap(~FltSvy, ncol = 10) +
  geom_vline(data = mean_talla, aes(xintercept = mean_Talla), 
             color = "red", 
             size = 0.7,
             alpha=0.5) +
  labs(title = "",
       x = "cm",
       y = "",
       fill = "Densidad") +
  theme_few()
```

@@

| Scenario | Description                                                                          |
|:------------:|:---------------------------------------------------------|
|    s1.1  | Spatial data without environmental and predator components                           |
|    s1.2  | "s1.1" with environmental and predator components                                    |
|    s1.3  | "s1.2" w/ selectivity blocks                                                         |

@@

# s1.2
r4ss::run(
  dir = dir1.2,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)

# s1.3
r4ss::run(
  dir = dir1.3,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)

```{r message=F, include=FALSE}
#s1.1
base.model1.1 <- SS_output(dir=dir1.1,
                        covar=T,
                        forecast=T)
#s1.2
base.model1.2 <- SS_output(dir=dir1.2,
                        covar=T,
                        forecast=T)
#s1.3
base.model1.3 <- SS_output(dir=dir1.3,
                        covar=T,
                        forecast=T)
```

```{r }
SSplotData(base.model1.1, 
           subplot = 1,
           pheight = 15)

SSplotData(base.model1.2, 
           subplot = 1,
           pheight = 15)
```
# RESULTS

```{r eval=FALSE, message=F, include=FALSE}
# Definir la ruta de la carpeta
folder_path <- "s1.1/plots"
# Verificar si la carpeta existe y eliminarla
if (dir.exists(folder_path)) {
  unlink(folder_path, recursive = TRUE)
  message("La carpeta 'plots' ha sido eliminada.")
} else {
  message("La carpeta 'plots' no existe.")
}

SS_plots(base.model1.1, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)

# S 1.2

# Definir la ruta de la carpeta
folder_path2 <- "s1.2/plots"
# Verificar si la carpeta existe y eliminarla
if (dir.exists(folder_path2)) {
  unlink(folder_path2, 
         recursive = TRUE)
  message("La carpeta 'plots' ha sido eliminada.")
} else {
  message("La carpeta 'plots' no existe.")
}

SS_plots(base.model1.2, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)

# S 1.3

# Definir la ruta de la carpeta
folder_path3 <- "s1.3/plots"
# Verificar si la carpeta existe y eliminarla
if (dir.exists(folder_path3)) {
  unlink(folder_path3, 
         recursive = TRUE)
  message("La carpeta 'plots' ha sido eliminada.")
} else {
  message("La carpeta 'plots' no existe.")
}

SS_plots(base.model1.3, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

### Main Variables poulation in `s1.1` scenario

```{r}
SSplotTimeseries(base.model1.1,
                 subplot = 1)
SSplotTimeseries(base.model1.1,
                 subplot = 9)
SSplotTimeseries(base.model1.1,
                 subplot = 7)
```

### Main Variables poulation in `s1.2` scenario

```{r}
SSplotTimeseries(base.model1.2,
                 subplot = 1)
SSplotTimeseries(base.model1.2,
                 subplot = 9)
SSplotTimeseries(base.model1.2,
                 subplot = 7)
```

### Main Variables poulation in `s1.3` scenario

```{r}
SSplotTimeseries(base.model1.3,
                 subplot = 1)
SSplotTimeseries(base.model1.3,
                 subplot = 9)
SSplotTimeseries(base.model1.3,
                 subplot = 7)
```

Selectivity

```{r fig.height=6}
SSplotSelex(base.model1.1,
            subplots = 1)

SSplotSelex(base.model1.2,
            subplots = 1)
```

@@

```{r}
SSplotComps(base.model1.2,
            subplots = 1)

@@

@@

```{r eval=FALSE}
total01 <- as.data.frame(base.model1.1$timeseries[1:31,c(2,5)]) %>%
  mutate(Serie = "No Spatial")
total1 <- as.data.frame(base.model1.2$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial implicit")
total2 <- as.data.frame(base.model2$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ without S-R relation")
total3 <- as.data.frame(base.model3$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation weak (0.9 steepness)")
total4 <- as.data.frame(base.model4$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation strong (0.6 steepness)")
total5 <- as.data.frame(base.model5$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation mid-strong estimated ")
total6 <- as.data.frame(base.model6$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ Ricker S-R relation estimated")
total7 <- as.data.frame(base.model7$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ New set parameters Linf, k and M")

@@

@@

```{r}
SSplotRunstest(base.model1.1,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
SSplotRunstest(base.model1.2,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

@@

```{r}
SSplotRunstest(base.model1.1,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1.2,
               subplots = "cpue",
               add=T)
```

@@

```{r eval=FALSE}
SSplotJABBAres(base.model01,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "len",
               add=T)
```

```{r}
SSplotJABBAres(base.model01,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "cpue",
               add=T)
```
## Relationship Stock-Recruit

@@

## Likelihood tables

@@

```{r echo=FALSE}
#read in all model runs
#note if cover=T you need a hessian; if covar=F you do not need a hessian
biglist1_2_3 <- SSgetoutput(keyvec = NULL,
                       dirvec = c(
                                  dir1.1,
                                  dir1.2,
                                  dir1.3),
                       getcovar = F)

#create summary of model runs from list above
summaryoutput1_2_3 <- SSsummarize(biglist1_2_3)

SSplotComparisons(summaryoutput1_2_3,
                  legendlabels = c("Ref Model: No Env-Predator",
                 "S1.1 w/ Predator data",
                 "S1.1 w/ Env and Predator data"),
                 filenameprefix = "COM1",
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,
                 plotdir=Figs)
```
